Prediction is Hard (Especially About the Future)

### 2015-08-14 Manuscript.tex
Updates from ShareLaTeX

\definecolor{Code}{rgb}{0,0,0}
\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
\definecolor{Numbers}{rgb}{0.5,0,0}
\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
\definecolor{Keywords}{rgb}{0,0,1}
\definecolor{self}{rgb}{0,0,0}
\definecolor{Strings}{rgb}{0,0.63,0}
\definecolor{Comments}{rgb}{0,0.63,1}
\definecolor{Comments}{rgb}{0.5,0.5,0.5}
\definecolor{Backquotes}{rgb}{0,0,0}
\definecolor{Classname}{rgb}{0,0,0}
\definecolor{FunctionName}{rgb}{0,0,0}
\definecolor{Operators}{rgb}{0,0,0}
\definecolor{Background}{rgb}{1,1,1}
\lstnewenvironment{code}[1]{
\lstset{
mathescape,
numbers=left,
numberstyle=\scriptsize,
stepnumber=1,
numbersep=0.5em,
xleftmargin=1em,
framextopmargin=2em,
framexbottommargin=2em,
showspaces=false,
showtabs=false,
showstringspaces=false,
tabsize=2,
% Basic
basicstyle=\ttfamily\scriptsize,
backgroundcolor=\color{Background},
language=Python,
% Comments
commentstyle=\color{Comments}\slshape,
% Strings
stringstyle=\color{Strings},
morecomment=[s][\color{Strings}]{"""}{"""},
morecomment=[s][\color{Strings}]{'''}{'''},
% keywords
morekeywords={[1]import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,None,access,as,,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert, dot, norm, zip, sorted},
keywordstyle={[1]\color{Code}\bfseries},
% additional keywords
morekeywords={[3]fastmap,Slope,bPruning,clister,train,leafs,weightedFeatures,HOW,envy, score,kNN,contrastSet,exemplar,Prune, exemplar,nearestSlope,dist,displace,geometry,splitAcross2Points,leaves,How,nearest,bPruning,Stats,divide,recurse,weight1,project, furthest, split,WHERE,clusterer, getContours,envied, fWeight, nearestContour, projection, mutate, HERE, knn},
keywordstyle={[3]\color{Keywords}\bfseries},
morekeywords={[2]@invari},
keywordstyle={[2]\color{Decorators}\slshape},
emph={self},
emphstyle={\color{self}\slshape},
firstnumber=last
%
}}{}

@@

\subsection{Finding Contrasts}
All the following methods use clustering in the form of WHERE, a top-down clustering method which recursively splits the data in two along a dimension that represents the highest variability, shown as Step-1 in figure \ref{fig:xtrees_bare}.

@@

\begin{figure}[t]
	\small
	~\hrule~

	{\bf Step 1: Top down clustering using WHERE}
	The data is recursively divided in clusters using WHERE as follows:
	\begin{itemize}

		\item Find   two   distance cases,  $X,Y$
		by picking any case $W$ at random, then setting $X$ to its most
		distant case, then setting $Y$ to the case most distant from
		$X$
		(this requires only $O(2N)$ comparisons
		of $N$ cases).
		\item Project each case $Z$
		onto a {\tt Slope} that  runs between $X,Y$ using the cosine
		rule. 
		\item Split the data at the median $X$ value of all cases and
		recurses on each half  (stopping when
		one half has less  than $\sqrt{N}$ of the original population).
	\end{itemize}

	~\hrule~

	{\bf Step 2: Distinguish between clusters using  decision trees}

	Call each leaf from WHERE a  ``class''. Use an entropy-based
	decision tree (DT) learner to learn what attributes select for each ``class''. To limit tree size:
	\bi
	\item Only use the top $\alpha=33$\%  of the features, as determined by their information gain~\cite{Irani1993}. 
	\item Only build the trees down to  max depth of $\beta=10$.
	\item Only build subtrees if it contains at least $N^{\gamma=0.5}$ examples (where $N$ is the size of the training set).
	\ei
	{\em Score}  DT  leaf nodes  via the mean score of its majority cluster.

	~\hrule~

	{\bf Step 3: Generating contrast sets from DT branches}
	\begin{itemize}
		\item Find the {\em current } cluster: take each test instance, run it down to a leaf in the DT tree.  
		\item Find the {\em desired} cluster: 
		\bi
		\item Starting at {\em current}, ascend the tree $lvl\in \{0,1,2...\}$ levels;
		\item Identify {\em sibling} clusters; i.e. leaf clusters that can be reached from level $lvl$ that are not {\em current }
		\item Using the {\em score} defined above, find the {\em better} siblings; i.e. those with a {\em score} less than $\epsilon=0.5$ times the mean score of {\em current}. If none found, then repeat for $lvl += 1$
		\item  Return the {\em closest} better sibling where distance is measured between the mean centroids of that sibling and {\em current}
		\ei
		\item Find the {\em delta}; i.e. the set difference between  conditions in the DT branch to {\em desired} and {\em current}. To find that delta:
		\bi
		\item
		For discrete attributes,  return the value from {\em desired}. 
		\item
		For  numerics, return the numeric difference. 
		\item
		For numerics  into ranges, return a random number selected from the low and high boundaries of the that range.
		\ei
		\ei
		~\hrule~
		\caption{CROSSTREES. Controlled by the parameters
			$\{\alpha, \beta, \gamma, \delta, \epsilon\}$ (set via engineering judgement).}
		\label{fig:xtrees_bare}
	\end{figure}

\subsection{DECISION TREES}

@@

\begin{figure*}[t]
\begin{minipage}{0.5\textwidth}
\includegraphics[width=0.9\linewidth]{Deltas-Ivy.eps}
\label{fig:delta_ivy}

\end{minipage}
\begin{minipage}{0.5\textwidth}
\includegraphics[width=0.9\linewidth]{Deltas-BDBJ.eps}
\label{fig:delta_apache}
\end{minipage}
\caption{Performance Comparison showing the number of times a certain feature requires to be changed. X-axis lists the various features that make up a data set. The y-axis contains the frequency of change in \%.}

\end{figure*}

@@

For the Jureczko OO data sets, we found:
\bi
\item
Most predictors in this domain were far from perfect;
\item 
But several of these predictors could
be salvaged using some sampling and optimization methods (see the notes on SMOTE and differential evolution, below).
\ei
As shown in \fig{j}, we   explore numerous examples of the Jureczko   object-oriented static code data sets: Ant, Camel, Ivy, Jedit,   Log4, Lucene, Poi, Synapse, Velocity, Xalan, Xerces\footnote{Available from the object-oriented defects section of the PROMISE respository openscience.us/repo/defect/ck.}. 
Given access to $V$ released
versions, we test on version $V$ and train on the available data from $V-1$ earlier releases (as
shown in \fig{j}, this means that we are training on hundreds to thousands
of classes and testing on smaller test suites).
Note the three bottom rows marked with $\times$: these contain predominately
defective classes (two-thirds, or more) and in such data sets, it is hard to distinguish
good from bad (since there are so many bad examples).

>>>>

\definecolor{Code}{rgb}{0,0,0}
\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
\definecolor{Numbers}{rgb}{0.5,0,0}
\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
\definecolor{Keywords}{rgb}{0,0,1}
\definecolor{self}{rgb}{0,0,0}
\definecolor{Strings}{rgb}{0,0.63,0}
\definecolor{Comments}{rgb}{0,0.63,1}
\definecolor{Comments}{rgb}{0.5,0.5,0.5}
\definecolor{Backquotes}{rgb}{0,0,0}
\definecolor{Classname}{rgb}{0,0,0}
\definecolor{FunctionName}{rgb}{0,0,0}
\definecolor{Operators}{rgb}{0,0,0}
\definecolor{Background}{rgb}{1,1,1}
\lstnewenvironment{code}[1]{
\lstset{
mathescape,
numbers=left,
numberstyle=\scriptsize,
stepnumber=1,
numbersep=0.5em,
xleftmargin=1em,
framextopmargin=2em,
framexbottommargin=2em,
showspaces=false,
showtabs=false,
showstringspaces=false,
tabsize=2,
% Basic
basicstyle=\ttfamily\scriptsize,
backgroundcolor=\color{Background},
language=Python,
% Comments
commentstyle=\color{Comments}\slshape,
% Strings
stringstyle=\color{Strings},
morecomment=[s][\color{Strings}]{"""}{"""},
morecomment=[s][\color{Strings}]{'''}{'''},
% keywords
morekeywords={[1]import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,None,access,as,,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert, dot, norm, zip, sorted},
keywordstyle={[1]\color{Code}\bfseries},
% additional keywords
morekeywords={[3]fastmap,Slope,bPruning,clister,train,leafs,weightedFeatures,HOW,envy, score,kNN,contrastSet,exemplar,Prune, FSel, exemplar,nearestSlope,dist,displace,geometry,splitAcross2Points,leaves,How,nearest,bPruning,Stats,divide,recurse,weight1,project, furthest, split,WHERE,clusterer, getContours,envied, fWeight, nearestContour, projection, mutate, HERE, knn},
keywordstyle={[3]\color{Keywords}\bfseries},
morekeywords={[2]@invari},
keywordstyle={[2]\color{Decorators}\slshape},
emph={self},
emphstyle={\color{self}\slshape},
firstnumber=last
%
}}{}

@@

\subsection{Finding Contrasts}
All the following methods use clustering in the form of WHERE, a top-down clustering method which recursively splits the data in two along a dimension that represents the highest variability. It works as follows:
\bi
\item Find   two   distance samples from the data, say  $X,Y$. This can be done by  picking any case $W$ at random, then setting $X$ to its most distant case, then setting $Y$ to the case most distant from $X$ (this requires only $O(2N)$ comparisons of $N$ cases).
\item Project each case $Z$ onto a {\tt Slope} that  runs between $X,Y$ using the cosine rule. 
\item Split the data at the median $X$ value of all cases and recurse on each half  (stopping when one half has less  than $\sqrt{N}$ of the original population).
\ei

@@

\input{tex/dtree.tex}
\subsection{DECISION TREES}

@@

\begin{figure}[t]
\begin{minipage}{0.5\textwidth}
\includegraphics[width=0.9\linewidth]{_figs/Deltas-Lucene.eps}
\label{fig:delta_ivy}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\includegraphics[width=0.9\linewidth]{_figs/Deltas-BDBJ.eps}
\label{fig:delta_apache}
\end{minipage}
\caption{Performance Comparison showing the number of times a certain feature requires to be changed. X-axis lists the various features that make up a data set. The y-axis contains the frequency of change in \%.}
\end{figure}

@@

For the Jureczko OO data sets, we found:
\bi
\item
Most predictors in this domain were far from perfect;
\item 
But several of these predictors could
be salvaged using some sampling and optimization methods (see the notes on SMOTE and differential evolution, below).
\ei
As shown in \fig{j}, we   explore numerous examples of the Jureczko   object-oriented static code data sets: Ant, Camel, Ivy, Jedit,   Log4, Lucene, Poi, Synapse, Velocity, Xalan, Xerces\footnote{Available from the object-oriented defects section of the PROMISE respository~\cite{promiserepo}.}. 
Given access to $V$ released
versions, we test on version $V$ and train on the available data from $V-1$ earlier releases (as
shown in \fig{j}, this means that we are training on hundreds to thousands
of classes and testing on smaller test suites).
Note the three bottom rows marked with $\times$: these contain predominately
defective classes (two-thirds, or more) and in such data sets, it is hard to distinguish
good from bad (since there are so many bad examples).
